Live Functional Programming with Typed Holes

### 2018-03-07 discussion.tex
note in discussion
Section 2, first full rough draft

@@

@@

>>>>

Weinberg from The Psychology of Computer Programming (1998): ``how truly sad it is that just at the very moment
when the computer has something important to tell us, it starts
speaking gibberish.''

@@

\rkc{something about visualizing hole environment traces}

@@

\rkc{quick mention that lazy evaluation with run-time exceptions for holes is
not enough. this would delay the failure a bit longer, but not indefinitely.}
